Investigating Police Citations in Houston

### 2023-04-16 draft4.Rmd
new plot scripts

legend("topright", legend=c("black", "white", "aapi", "unknown"), col=c("blue", "red", "green", "orange"), pch = 20, cex = 0.7, title = "Race")

@@

```{r, echo=FALSE}
#mini_htx2 <- mini_htx[seq(1,666666,6),]
mini_htx2$diff <- abs(mini_htx2$speed - mini_htx2$posted_speed)
mini_htx3 <- mini_htx2[, c("date", "diff")]
mini_htx3 <- na.omit(mini_htx3)
mini_htx3 <- mini_htx3[mini_htx3$diff != 693,]

>>>>

  other <- race_date[race_date$subject_race=="other",]
  other$year <- unlist(lapply(other$date, year_only))
  points(sort(unique(other$year)), as.vector(table(as.factor(other$year))))
  lines(sort(unique(other$year)), as.vector(table((as.factor(other$year)))), 
        type = "l", col = "purple")

legend("topright", legend=c("black", "white", "aapi", "unknown", "other"), col=c("blue", "red", "green", "orange", "purple"), pch = 20, cex = 0.7, title = "Race")

@@

```{r, echo=FALSE}
#mini_htx2 <- mini_htx[seq(1,666666,6),]

mini_htx2$diff <- abs(mini_htx2$speed - mini_htx2$posted_speed)
mini_htx3 <- mini_htx2[, c("date", "diff")]
mini_htx3 <- na.omit(mini_htx3)
mini_htx3 <- mini_htx3[mini_htx3$diff != 693,]
